Certified Desugaring of Javascript Programs using Coq

### 2016-12-14 paper/paper.tex
more progress on the introduction

\usepackage[backend=biber,bibencoding=utf8]{biblatex}

@@

Note that we do not prove the converse, i.e., that if a JavaScript program has a
semantic in JSCert, then its \lambdajs translation successfully terminates and
the results match. The reason is technical and is described in
Section~\ref{sec:coq-techniques} alongside the techniques we implemented in Coq
for this development.

To reduce the complexity of the task, we are currently working
only on proving \lambdajs correct with respect to JSCert,
i.e., that if the \lambdajs program successfully terminates,
then its result matches the result given by JSCert. We are also
restricting our attention to ECMAScript strict mode, proving the
correctness of non-strict features only when it is convenient.
\asi{We should have a sentence like ``Proving the other direction requires doing
  an inversion of the full JSCert semantics. Unfortunately, the techniques we
  have used (see Section $\ldots$) do not scale to semantics of that size.'' }

We were able to prove correctness of a large part of the
JavaScript semantics, including function calls, lexical environment
handling, and most operations involving objects. The work is still
in progress to prove the remaining parts, which include integer
operations, the
defineOwnProperty method, and elements of the standard library.

The development is publicly available and can be downloaded from GitHub:

\url{https://github.com/tilk/LambdaCert}

@@

>>>>

\usepackage[backend=biber,bibencoding=utf8,urldate=iso8601,date=iso8601]{biblatex}

@@

Note that we do not prove the converse, i.e., that if a JavaScript program has a
semantic in JSCert, then its \lambdajs translation successfully terminates and
the results match. For such a result, we would need to apply \textsf{inversion}
on the full JSCert semantics, which does not currently work. This issue is
described in Section~\ref{sec:coq-techniques} alongside the techniques we
implemented in Coq for this development.

The development is publicly available and can be downloaded from
GitHub~\cite{github:lambdacert}.

@@

\asi{This was in the introduction, we need to integrate it again.

We were able to prove correctness of a large part of the
JavaScript semantics, including function calls, lexical environment
handling, and most operations involving objects. The work is still
in progress to prove the remaining parts, which include integer
operations, the
defineOwnProperty method, and elements of the standard library.
}
